---
title: "SparkR Tutorial"
output: ioslides_presentation
---

## SparkR

R on Spark

make Data Analysis easier, faster and interesting

## Show a Demo

a simple Demo:

How are our users distributed by province ?

Let's start !

## Where to start ?

Rstudio: a web R IDE

http://hadoop.corp.mediav.com:8787/

UserName: datascientist
Password: mediav

## setup SparkR env

```{r}
Sys.setenv(SPARK_HOME = '/opt/spark-1.4.1-mv')
Sys.setenv(SPARK_YARN_QUEUE = "bi")
library("SparkR")
```

## init SparkR

```{r}
sc = sparkR.init()
hiveContext = sparkRHive.init(sc)
```

## First Demo - cookie distribution by province

```{r}
cookiesByProvinceid_df = sql(
  hiveContext, "select geo_info.province as provinceid, 
  count(cookie) as cookies from mediav_base.d_clickvalue 
  where date='2015-07-07' and geo_info.country=1 group by geo_info.province"
)
cache(cookiesByProvinceid_df)
head(cookiesByProvinceid_df,n=2)

registerTempTable(cookiesByProvinceid_df,"cookiesByProvinceid")
```

## Transform provinceid to ADCODE99

``` {r}

# join mediav_base_location for provincename and geoid
cookiesByProvicename_df = sql(
  hiveContext,"select c.provinceid, c.cookies, l.en, l.geoid 
  from cookiesByProvinceid c left join mysql.mediav_base_location l 
  on c.provinceid=l.ID"
)
cache(cookiesByProvicename_df)
cookiesByProvicename = collect(cookiesByProvicename_df)

# geoid -> ADCODE99
ADCODE99 = substr(cookiesByProvicename$geoid,5,10)

# cbind, got a new data frame demonstrating num of cookies by province with province ADCODE99
cookiesByProvicename_withADCODE99 = cbind(cookiesByProvicename,ADCODE99)

```

## plotting - import library

```{r}
library(maptools)
library(ggplot2)
library(plyr)
gpclibPermit()
```

## plotting - load china map

```{r}
# load china map data
china_map = readShapePoly("mapdata/bou2_4p.shp")
# just plot it
plot(china_map)
```

## plotting - prepare china map data

```{r}
x = china_map@data          #get location data
xs = data.frame(x,id = seq(0:924) - 1)          # 925 locations
china_map1 = fortify(china_map)           # fortify to data frame
china_map_data = join(china_map1, xs, type = "full")       #join two data frame
china_map_data$NAME = iconv(china_map_data$NAME, from = "GBK")　# convert NAME to UTF8
```

## plotting - prepare cookie distribution data on map

```{r}
cookiesByProvicename_map_data = join(china_map_data,
                                     cookiesByProvicename_withADCODE99, 
                                     type = "right")
# clean up NA
cookiesByProvicename_map_data[is.na(cookiesByProvicename_map_data)] <-  0
```

## plotting -  show sample data

```{r}
head(cookiesByProvicename_map_data, n=2)

```

## plotting - visualize it 
```{r, echo=FALSE}
# plot it, this is the final map of cookies distribution of china by province
viz = ggplot(cookiesByProvicename_map_data, aes(
  x = long, y = lat, group = group,fill = cookies
)) +
  geom_polygon(colour = "grey40") +
  scale_fill_gradient(low = "white",high = "steelblue") + 
  theme(
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) +
  labs(title = "Cookie Distribution of China By Province")
viz
```

## How you feel about this Data Analysis Job?

* Easy: you do not need build a maven job, build it, and deploy. 
       Just write a R script, most code logic can be implemented by SQL.
* Fast: about *10 min* overall
* Interesting: visualize the data, easier to understand

## Further more

Data Visualization is important !

1. intesting retargeting analysis

How are users *who are interesting in MacBook* distributed by province ?

2. ROI Trend 

How is the ROI thrend of last month of a specific adspace ?